Twists of supersymmetric gauge theories

### 2019-09-11 paper.tex
Added a remark on a suggestion Brian made

>>>>

\chris{Brian's suggestion to avoid this second calculation is as follows.  By assumption, the holomorphically twisted theory will be equivariant for $\SU(n) \ltimes \CC^n$.  It is also expected to be a cotangent theory, so equivariant for the $\CC^\times$ action that scales the cotangent fiber.  Brian says that he knows how to calculate the cohomology group corresponding to interactions equivariant for this group, and that it will be one-dimensional.  As a consequence, the holomorphic twist will have an action which is automatically cohomologous to the expected answer.  It remains to show that the twisted theory is $\CC^\times$-equivariant.  The $\CC^\times$ action we should consider is the one where BRST fields have weight 0 and their antifields have weight 1.}
